% Options for packages loaded elsewhere
% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  16,
]{article}
\usepackage{xcolor}
\usepackage[top=15mm,left=15mm,right=15mm,bottom=15mm,heightrounded]{geometry}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage[]{libertinus}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother


\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother





\setlength{\emergencystretch}{3em} % prevent overfull lines

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}



 


\usepackage{multicol}
\usepackage{lipsum}
\usepackage{hyperref}
\pagestyle{empty}
\usepackage{fontawesome5}
\usepackage{marvosym}
\setlength{\multicolsep}{2pt plus 1.0pt minus 0.75pt}% 50% of original values
\usepackage{vwcol}
\setlength{\columnsep}{3em}
\pagestyle{plain}
\setcounter{page}{1}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}


\author{}
\date{}
\begin{document}


\begin{huge}\begin{center}{\bf SANGHOON PARK}\end{center}\end{huge}

\begin{center}
{\faEnvelope} \href{sh.park.poli@gmail.com}{\ttfamily sh.park.poli@gmail.com} ∙
{\faLink} \href{sanghoon-park.com}{\ttfamily sanghoon-park.com} ∙ 
{\faGithub} \href{https://github.com/pherephobia}{\ttfamily github.com/pherephobia}
\end{center}
\vspace{15pt}
\vspace{3pt}
\begin{large}
 {\bf ACADEMIC APPOINTMENTS}
  \vspace{3pt}
  \hrule
  \begin{minipage}[c]{0.6\textwidth}
    \begin{flushleft}{\href{https://wwwk.kangwon.ac.kr/english/index.do}{\bf Kangwon National University}}\end{flushleft}
  \end{minipage}
  \begin{minipage}[c]{0.39\textwidth}
    \begin{flushright}Aug 2024-Present\end{flushright}
  \end{minipage}
  \vspace{-0.17cm}
  \begin{minipage}[c]{0.6\textwidth}
    \begin{flushleft}Senior Researcher, \href{https://kius.kangwon.ac.kr/}{Kangwon Institute for Unification Studies}\end{flushleft}
  \end{minipage}
  \begin{minipage}[c]{0.39\textwidth}
    \begin{flushright}Chuncheon, ROK\end{flushright}
  \end{minipage}
  \vspace{-0.25cm}
\end{large}
\vspace{3pt}

\vspace{3pt}
\begin{large}
 {\bf EDUCATION}
  \vspace{3pt}
  \hrule
  \begin{multicols}{2}
    \begin{flushleft}{\bf University of South Carolina}\end{flushleft}
    \begin{flushright}Dec. 2024\end{flushright}
  \end{multicols}
  \vspace{-0.17cm}
  \begin{multicols}{2}
    \begin{flushleft}Ph.D. in Political Science\end{flushleft}
    \begin{flushright}Columbia, SC\end{flushright}
  \end{multicols}
  \vspace{-0.25cm}
  \hspace{3pt}\textit{Fields for Comprehensive Exams:}\\
  \vspace{-0.25cm}
  \hspace{6pt}\textit{Comprative Politics} (Major, passed with distinction), \textit{International Relations} (Minor)
\end{large}
\vspace{3pt}

\vspace{7pt}
\begin{large}
   \begin{multicols}{2}
    \begin{flushleft}{\bf Hankuk University of Foreign Studies}\end{flushleft}
    \begin{flushright}Feb. 2017\end{flushright}
  \end{multicols}
  \vspace{-0.17cm}
  \begin{multicols}{2}
    \begin{flushleft}M.A.: Political Science and International Relations\end{flushleft}
    \begin{flushright}Seoul, ROK\end{flushright}
  \end{multicols}
  \vspace{-0.25cm}
  \hspace{3pt}Advisor: Dr. Jaemook Lee (Political Science), and specially Daejin Yi (Political Science)
\end{large}
\vspace{3pt}

\begin{large}
  \begin{multicols}{2}
    \begin{flushleft}{\bf Hankuk University of Foreign Studies}\end{flushleft}
    \begin{flushright}Feb. 2015\end{flushright}
  \end{multicols}
  \vspace{-0.17cm}
  \begin{multicols}{2}
    \begin{flushleft}B.A.: Political Science and International Relations\end{flushleft}
    \begin{flushright}Seoul, ROK\end{flushright}
  \end{multicols}
\end{large}
\vspace{7pt}

\begin{large}{\bf RESEARCH INTERESTS}
  \vspace{3pt}
  \hrule
  \begin{multicols}{2}
    \begin{flushleft}{\bf Comparative Politics}\end{flushleft}
    \begin{flushright}\end{flushright}
  \end{multicols}
\end{large}
\vspace{-0.16cm}

\begin{itemize}
\tightlist
\item
  Authoritarian Regimes, Regime Survival, Comparative Institutions,
  Political Economics of Inequality and Redistribution, International
  Human Rights, Forced Migration
\end{itemize}

\vspace{7pt}

\begin{large}
  \begin{multicols}{2}
    \begin{flushleft}{\bf International Relations}\end{flushleft}
    \begin{flushright}\end{flushright}
  \end{multicols}
\end{large}
\vspace{-0.16cm}

\begin{itemize}
\tightlist
\item
  Democratic Diffusion, Naming and Shaming as a Autocratic
  Legitimization Strategy, Human Rights, Economic Shocks and Sanctions
\end{itemize}

\vspace{7pt}

\begin{large}{\bf TEACHING INTERESTS}
  \vspace{3pt}
  \hrule
  \begin{multicols}{2}
    \begin{flushleft}{\bf Comparative Politics}\end{flushleft}
    \begin{flushright}\end{flushright}
  \end{multicols}
\end{large}
\vspace{-0.16cm}

\begin{itemize}
\tightlist
\item
  Introduction to Comparative Politics, Democracy and Dictatorship,
  Comparative Institutions
\end{itemize}

\vspace{7pt}

\begin{large}
  \begin{multicols}{2}
    \begin{flushleft}{\bf International Relations}\end{flushleft}
    \begin{flushright}\end{flushright}
  \end{multicols}
\end{large}
\vspace{-0.16cm}

\begin{itemize}
\tightlist
\item
  Introduction to International Relations
\end{itemize}

\vspace{7pt}

\begin{large}
  \begin{multicols}{2}
    \begin{flushleft}{\bf Political Methodology}\end{flushleft}
    \begin{flushright}\end{flushright}
  \end{multicols}
\end{large}
\vspace{-0.16cm}

\begin{itemize}
\tightlist
\item
  Introduction to Statistical Methods for Political Science
\end{itemize}

\vspace{7pt}

\begin{large}{\bf PEER-REVIEWED ARTICLES} (SCOPUS \& SSCI)
  \vspace{3pt}
  \hrule
\end{large}
  \begin{itemize}
    \item[7.] \textbf{Park, Sanghoon}, Chun Young Park, and Hyunkyu Kim. 2026.~``Manufacturing Compliance: How Pariah States Strategically Engage with International Human Rights Mechanisms.'' \textit{International Political Science Review. Forthcoming}.
    \item[6.] \textbf{Park, Sanghoon}. 2025. ~``Why Do Authoritarian Regimes Provide Welfare?'' \textit{Democratization}. \textbf{Accepted}, DOI: \href{https://doi.org/10.1080/13510347.2025.2592090}{https://doi.org/10.1080/13510347.2025.2592090} [SSCI]
    \item[5.] \textbf{Park, Sanghoon}, Won Mo Jang, Hyun-Hee Heo, Deok Hyun Jang, and Jaeyoung Hur. 2025. ~``Retrospection and Vote Choice: Evidence from Cross-sectional Studies in South Korea.'' \textit{Asian Perspective} 49(3): 533-572, DOI:  \href{https://doi.org/10.1353/anp.2025.a968244}{https://doi.org/10.1353/anp.2025.a968244}. [SSCI]
    \item[4.] Heinrich, Tobias, Spencer Baily, Kuan-wu Chen, Jack DeOliveira, \textbf{Sanghoon Park}, and Navida Chun-han Wang. 2025. ~``AI-Assisted Grading and Personalized Feedback in Large Political Science Classes: Results from Randomized Controlled Trials.'' \textit{PLOS One}. 20(8): e0328041, DOI:  \href{https://doi.org/10.1371/journal.pone.0328041}{https://doi.org/10.1371/journal.pone.0328041}. [SCI]
    \item[3.] Park, Chun-Young and \textbf{Sanghoon Park}. 2025. ~``You Scratch My Back, and I Scratch Yours: An Explanation of Dyadic Politics of Naming and Shaming.'' \textit{International Interactions} 51(1): 1-28. DOI: \href{https://doi.org/10.1080/03050629.2024.2421498}{10.1080/03050629.2024.2421498} [SSCI]
    \item[2.] Kim, Hyunkyu and \textbf{Sanghoon Park}. 2024. ~``\href{https://doi.org/10.1007/s11366-024-09886-2}{Expanding China’s Influence via Membership: Examining the Influence of Chinese-Led International Institutions on Responses to Human Rights Issues in China}." \textit{Journal of Chinese Political Science}. DOI: \href{https://doi.org/10.1007/s11366-024-09886-2}{10.1007/s11366-024-09886-2}. [SSCI]
    \item[1.] Wilson, Matthew, Christopher Howell, Kelsey Martin-Morales, and \textbf{Sanghoon Park}. 2023. ~``\href{https://www.tandfonline.com/doi/full/10.1080/15512169.2023.2164861}{Concept Mapping and Reading Comprehension}." \textit{Journal of Political Science Education.} DOI: \href{https://doi.org/10.1080/15512169.2023.2164861}{10.1080/15512169.2023.2164861}. [SCOPUS]
\end{itemize}

\vspace{7pt}

\begin{large}{\bf PEER-REVIEWED ARTICLES} (KCI)
  \vspace{3pt}
  \hrule
\end{large}
  \begin{itemize}
    \item[21.] \textbf{Park, Sanghoon}, and Young Hoon Song.  2026. ~``When Does Summit Diplomacy Make Peace? An Empirical Analysis of the Conditional Effects of Summit Format, Regime Type, and Interstate Rivalry.'' \textit{The Journal of Peace Studies} 27(1): forthcoming.
    \item[20.] \textbf{Park, Sanghoon}, Song Young Hoon, and Hyeonjun Kim. 2026, ~``The Interaction of Authoritarian and Populist Orientations on Attitudes toward Refugees.'' \textit{The Journal of Political Science \& Communication} 29(1): 69-106.
    \item[19.] Kong, Seonju, Seungji Lee, Young Hoon Song, and \textbf{Sanghoon Park}. 2025. ~``Motivations for Humanitarian Assistance Activists' Participation in Public Education in South Korea.'' \textit{Korean Journal of International Migration} 12(2): 147-174.
    \item[18.] \textbf{Park, Sanghoon}, Young Hoon Song, Dongeun Shin. 2025.  ~``Multidimensional Boundaries of Perception toward Refugees as Outgroup in South Korea.''  \textit{Journal of Future Politics} 15(2): 1-24. 
    \item[17.] Lim, Yoojin, Young Hoon Song, and \textbf{Sanghoon Park}. 2025. ~``Refugee Act and Legislative Politics in South Korea: Who Engages and in Which Refugee Bills?'' \textit{Korean Journal of Legislative Studies (KJLS)}. 31(2): 129-164.
    \item[16.] Song, Young Hoon, and \textbf{Sanghoon Park}. 2025. ~``Social Integration of North Korean Defectors in South Korea and Changes in Perceptions of Social Distance by Relationship.'' \textit{Journal of Northeast Asian Studies (JNAS)} 30(2): 137-154.
    \item[15.] Yoojin Lim, and \textbf{Sanghoon Park}. 2025. ~``Beyond Yes or No: Cognitive-Knowledge Gap and Conditional Refugee Attitudes in South Korea.'' \textit{Studies in Humanities and Social Sciences} 68(2): 5-30. DOI: \href{https://doi.org/10.17939/hushss.2025.68.2.001}{10.17939/hushss.2025.68.2.001}
    \item[14.] Song, Young Hoon, Yoojin Lim, and \textbf{Sanghoon Park}. 2025. ~``2024 Korean Refugee Perception Survey: A Preliminary Study for Establishing a Long-Term Database.'' \textit{Journal of Research Methodology} 30(1): 223-254.
    \item[13.] \textbf{Park, Sanghoon}, and Da Bin Jung. 2023. ~``Voter Choices in Re/By-Elections: A Study of Local Re/By-Elections Between 2010 and 2021." \textit{Korean Party Studies Review} 22(4): 71-95.
    \item[12.] \textbf{Park, Sanghoon}, Chaehoon Lee, amd Ilgi Kim. 2023. ~``A Study on the Prevention Legislation for Strengthening Technology Security: Focusing on Global Legislative Cases Related to National Technology Security." \textit{Journal of National Intelligence Studies} 16(2): 37-82.
    \item[11.] \textbf{Park, Sanghoon}, and Jaeyoung Hur. 2023. ~``Who Does Early Voting Serve?: A Study of Voters in Korea’s 20th Presidential Election." \textit{JOURNAL OF FUTURE POLITICS} 13(1): 181-211.
    \item[10.] \textbf{Park, Sanghoon}, and Chaehoon Lee. 2023. ~``Multi-Member District and Survival of the Third Party: The Cases between the 4th and 8th Korean Local Elections." \textit{The Study of Election (NEC)} 18(1): 5-32. DOI: \href{https://doi.org/10.23018/nec.2023.1.18.001}{10.23018/nec.2023.1.18.001}
    \item[9.] \textbf{Park, Sanghoon}. 2022. ~``\href{http://www.partystudies.or.kr/contents/bbs/bbs_list.html?bbs_cls_cd=004003}{Effect of reasons for re-election on voting participation and outcomes: An empirical examination of re/by-elections for the Korean National Assembly after democratization.}"  \textit{Korean Party Studies Review} 21(3): 41-80.
\item[8.] Kang, Jiyoon, \textbf{Sanghoon Park}, and Sun Gue Yang. 2022. ~``\href{http://basicdata.kr/board/read/journals/146/}{Leadership in Communication:
How Leadership and Communication Affect Public Service Motivation (PSM)}." \textit{Journal of Research Methodology} 7(1): 23-60.
\item[7.] \textbf{Park, Sanghoon}, Chaehoon Lee, and Ilgi Kim. 2020. ~``\href{https://www.earticle.net/Journal/Issues/511/28448}{Infectious Disease Management and New Security Strategies: The Case of African Swine Fever in South Korea}." \textit{The Journal of Peace Studies} 21(2): 143-174.
\item[6.] \textbf{Park, Sanghoon}, and Jaeyoung Hur. 2020. ~``\href{http://www.discourse201.org/html/sub05_01.asp}{Does North Korea Policies Reflect Public Opinion? The Public Awareness Survey Around the 4.27 Panmunjom Declaration}." \textit{Discourse 201} 23(2): 83-113.
\item[5.] Lee, Jaehoon, and \textbf{Sagnhoon Park}. 2020. ~``\href{https://m.nec.go.kr/portal/cmm/fms/FileDown.do?atchFileId=5d0ffae936edc42f3b4e864801f86a0f4096c44da03fede418b94067e8f9d0ea&fileSn=1&bbsId=&searchYear=}{Climate and Electoral Participation: The Effect of Particulate Matter on Election in South Korea}'' \textit{The Study of Election} 12(1): 77-98.
\item[4.] \textbf{Park, Sanghoon}, Jaemook Lee, and Daejin Yi. 2017.``Dictatorships and Redistribution: Empirical Analysis of Redistribution by Dictatorships Sub-regime Type.'' \textit{OUGHTOPIA} 32(1), 271-314.
\item[3.] Oh, Sujin, \textbf{Sanghoon Park}, and Jaemook Lee. 2017. ~``Class Betrayal Voting and Political Knowledge in the 20th Korean General Election.'' \textit{Korean Political Science Review} 51(1), 153-180.
\item[2.] Park, Youngdeuk, \textbf{Sanghoon Park}. 2016. \href{http://kiss.kstudy.com/thesis/thesis-view.asp?key=3472800}{``Determinants of Voting Choice in Brexit Referendum: Skill Level and Job Competition in the Labor Market."} \textit{The Korean Journal of Area Studies} 34(3), 1-31.
\item[1.] \textbf{Park, Sanghoon}. 2015. \href{http://search.koreanstudies.net/thesis/thesis-view.asp?key=3438155}{``Welfare Expenditure and Economic Growth: The Sub-types of Welfare Expenditure of OECD countries."} \textit{Global Political Research} 9(2), 81-107.
\end{itemize}

\vspace{7pt}

\begin{large}{\bf OTHER PUBLICATIONS}
  \vspace{3pt}
  \hrule
\end{large}
\begin{itemize}
  \item[3.] Hashimoto, Barry, \textbf{Sanghoon Park}, Victor Y. Wu. 2024. ~``Computational Reproducibility of \'\'The Impact of Presidential Appointment of Judges: Montesquieu or the Federalists?\'\''' \textit{I4R Discussion Paper Series}, No. 135, Institute for Replication (I4R), s.l., \href{https://hdl.handle.net/10419/300276}{https://hdl.handle.net/10419/300276}.
  \item[2.] Wilson, Matthew and \textbf{Sanghoon Park}. 2022. ~``Empirical Indicators of Democracy and Authoritarianism.'' In {\it Oxford Bibliographies in Political Science}. Ed. Sandy Maised. New York: Oxford University Press. DOI: \href{https://www.oxfordbibliographies.com/display/document/obo-9780199756223/obo-9780199756223-0348.xml}{10.1093/OBO/9780199756223-0348}.
    \item[1.] \textbf{Park, Sanghoon} and Jaeyoung Hur. 2021. ~``What do we know and do not know?: Attitudes toward North Korea and unification.'' In {\it Issues and Perspectives in Korean Peace Process.} Hankuk University of Foreign Studies Knowledge Contents \& Press.
\end{itemize}
\vspace{-0.16cm}

\vspace{7pt}

\begin{large}{\bf UNDER REVIEWS}

  \vspace{3pt}

  \hrule

\end{large}
\begin{itemize}

  \item[2,] ~``Seeing but Not Chaning: Reinforcement of Negative Attitudes toward Refugees in South Korea." (with Hyeonjun Kim, Se Hyeon Sim at Kangwon Institute for Unification Studies, Kangwon National University, \& Young Hoon Song at Kangwon National University) 
  \item[1.] ~``Thriving in Confinement: What Enables Rohingya Refugee Women's Economic Empowerment in Cox's Bazar." (with Seungji Lee, Yoojin Lim, \& Young Hoon Song at Kangwon National University)

\end{itemize}

\vspace{7pt}

\begin{large}{\bf INVITED TALKS}
  \vspace{3pt}
  \hrule
\end{large}
\begin{itemize}
\item 2024. \href{https://pherephobia.github.io/3_NazarbayevDS/}{PLS412/512 Data Visualization Special Lecture}. Political Science and International Relations, Nazarbayev University, Kazakhstan, February 6th.
\end{itemize}

\vspace{7pt}

\begin{large}{\bf WORKS IN PROGRESS}
  \vspace{3pt}
  \hrule
\end{large}
\begin{itemize}
    \item[4.] ~``Inner Circles and Open Borders: The Institutional Logic of refugee in Autocracies."
    \item[3.] ~``Rallying Solidarity: Why Economic Sanctions Fail." (with Jaeyoung Hur, Taehee Whang at Yonsei University \& Hannah Kim at Sogang University)
    \item[2.] ~``The Appointment of Female Ministers in Asian Autocracies." (with Ha Eun Choi at Michigan State University)
    \item[1.] ~``Party Institutionalization and Civil Conflict." (with Dr. Matthew C. Wilson at University of South Carolina)
%    \item[2.] ~``Digital Technology and the Choice to Repress or Co-opt." (with Emily Harmon and Kuanwu Chen at University of South Carolina)
    % \item[3.] ~``Heterogeneous Democratization: Elite Politics and Economic Sanctions."
%   \item[4.] ~``Why Some Authoritarian Regimes Grow More than Other Authoritarian Regimes?."
%   \item[3.] ~``When Democratic Breakdown Happens? Inequality and Democratic Consolidation."
    % \item[1.] ~``The Welfare States without Labor in Asia: Power Resources Theory Revisited."
%   \item[1.] ~``Labor condition and the society: instability and ㅑnfertility, the conditional effects of labor protection."
\end{itemize}

\vspace{7pt}

\begin{large}{\bf HONORS, AWARDS, AND GRANTS}
  \vspace{3pt}
  \hrule
  \begin{multicols}{2}
    \begin{flushleft}{\bf Walker Institute}\end{flushleft}
    \begin{flushright}Apr-Sep 2024\end{flushright}
  \end{multicols}
  \vspace{-0.17cm}
  \begin{multicols}{2}
    \begin{flushleft}\textit{University of South Carolina}\end
    {flushleft}\begin{flushright}Columbia, SC\end
    {flushright}
  \end{multicols}
  \end{large}
\vspace{-0.16cm}

\begin{itemize}
\tightlist
\item
  \href{https://sc.edu/study/colleges_schools/artsandsciences/walker_institute/research/student_scholarships_and_grants/index.php}{Seung Yeun Kim Graduate Fellowship}
  (\$3,000)
\end{itemize}

\vspace{7pt}

\begin{large}
  \begin{multicols}{2}
    \begin{flushleft}{\bf Institute for Humane Studies}\end{flushleft}
    \begin{flushright}Mar-July 2024\end{flushright}
  \end{multicols}
  \vspace{-0.17cm}
  \begin{multicols}{2}
    \begin{flushleft}\textit{George Mason University}\end
    {flushleft}\begin{flushright}Arlington, VA\end
    {flushright}
  \end{multicols}
\end{large}
\vspace{-0.16cm}

\begin{itemize}
\tightlist
\item
  Humane Studies Fellowship (IHS017856, \$2,500)
\end{itemize}

\begin{large}
  \begin{multicols}{2}
    \begin{flushleft}{\bf Institute for Humane Studies}\end{flushleft}
    \begin{flushright}Sep 2023-May 2024\end{flushright}
  \end{multicols}
  \vspace{-0.17cm}
  \begin{multicols}{2}
    \begin{flushleft}\textit{George Mason University}\end
    {flushleft}\begin{flushright}Arlington, VA\end
    {flushright}
  \end{multicols}
\end{large}
\vspace{-0.16cm}

\begin{itemize}
\tightlist
\item
  Humane Studies Fellowship (IHS017655, \$5,000)
\end{itemize}

\vspace{7pt}

\begin{large}
  \begin{multicols}{2}
    \begin{flushleft}{\bf Walker Institute}\end{flushleft}
    \begin{flushright}Apr-Sep 2023\end{flushright}
  \end{multicols}
  \vspace{-0.17cm}
  \begin{multicols}{2}
    \begin{flushleft}\textit{University of South Carolina}\end
    {flushleft}\begin{flushright}Columbia, SC\end
    {flushright}
  \end{multicols}
\end{large}
\vspace{-0.16cm}

\begin{itemize}
\tightlist
\item
  \href{https://sc.edu/study/colleges_schools/artsandsciences/walker_institute/research/student_scholarships_and_grants/index.php}{Seung Yeun Kim Graduate Fellowship}
  (\$3,000)
\end{itemize}

\vspace{7pt}

\begin{large}
  \begin{multicols}{2}
    \begin{flushleft}{\bf EITM Institute}\end{flushleft}
    \begin{flushright}June-Jul 2022\end{flushright}
  \end{multicols}
  \vspace{-0.17cm}
  \begin{multicols}{2}
    \begin{flushleft}\textit{University of California, Berkeley}\end
    {flushleft}\begin{flushright}Berkeley, CA\end
    {flushright}
  \end{multicols}
\end{large}
\vspace{-0.16cm}

\begin{itemize}
\tightlist
\item
  \href{https://eitminstitute.org/institute/2022/}{2022 EITM Summer Institute}
  (\$750)
\end{itemize}

\vspace{7pt}

\begin{large}
  \begin{multicols}{2}
    \begin{flushleft}{\bf EITM Institute}\end{flushleft}
    \begin{flushright}June-Aug 2020\end{flushright}
  \end{multicols}
  \begin{multicols}{2}
    \begin{flushleft}\textit{University of Michigan, Ann Arbor}\end
    {flushleft}\begin{flushright}Ann Arbor, MI\end
    {flushright}
  \end{multicols}
\end{large}
\vspace{-0.16cm}

\begin{itemize}
\tightlist
\item
  \href{https://52.2.147.143/icpsrweb/content/sumprog/scholarships/winners-2020.html}{EITM Certification Scholarships}
\item
  Both sessions at the ICPSR Summer Program (\$4,000)
\end{itemize}

\vspace{7pt}

\begin{large}
  \begin{multicols}{2}
    \begin{flushleft}{\bf University of South Carolina}\end{flushleft}
    \begin{flushright}2020\end{flushright}
  \end{multicols}
  \vspace{-0.17cm}
  \begin{multicols}{2}
    \begin{flushleft}\textit{Department of Political Science}\end
    {flushleft}\begin{flushright}Columbia, SC\end
    {flushright}
  \end{multicols}
\end{large}
\vspace{-0.16cm}

\begin{itemize}
\tightlist
\item
  Outstanding Graduate Student Awards
\item
  The Second Annual Conference Funding Competition: Joint award (\$500)
\end{itemize}

\vspace{7pt}

\begin{large}{\bf RESEARCH EXPERIENCE}
  \vspace{3pt}
  \hrule
  \begin{multicols}{2}
    \begin{flushleft}{\bf Graduate Research Assistant}\end{flushleft}
    \begin{flushright}2023-Present\end{flushright}
  \end{multicols}
  \vspace{-0.17cm}
  \begin{multicols}{2}
    \begin{flushleft}\textit{Comparative Political Regimes Lab}\end{flushleft}
    \begin{flushright}Tuscaloosa, AL and Columbia, SC\end{flushright}
  \end{multicols}
  \end{large}
\vspace{-0.16cm}

\begin{itemize}
\tightlist
\item
  The Comparative Political Regimes (CPR) Lab
  (\href{https://acrowinghen.com/cpr/}{\ttfamily https://acrowinghen.com/cpr/})
  investigating regimes and regime transformation from a comparative
  perspective.
\item
  Principal investigator: Professor Amanda B. Edgell (Political Science,
  University of Alabama) and Professor Wilson C. Matthew (Political
  Science, University of South Carolina)
\end{itemize}

\begin{large}{\bf TEACHING EXPERIENCE}
  \vspace{3pt}
  \hrule
  \begin{multicols}{2}
    \begin{flushleft}{\bf Instructor}\end{flushleft}
    \begin{flushright}2024-2025\end{flushright}
  \end{multicols}
  \vspace{-0.17cm}
  \begin{multicols}{2}
    \begin{flushleft}\textit{Kangwon National University}\end{flushleft}
    \begin{flushright}Chuncheon, ROK\end{flushright}
  \end{multicols}
  \end{large}
\vspace{-0.16cm}

\begin{itemize}
\tightlist
\item
  Fall 2025: Theories of Democracy (U)
\item
  Fall 2025: Politics and Data Analysis (U)
\item
  Spring 2025: Comparative Politics (U)
\item
  Spring 2025: Designing Political Inquiry (U)
\item
  Fall 2024: Politics and Society (U)
\item
  Fall 2024: Political Process
\end{itemize}

\vspace{7pt}

\vspace{3pt}

\begin{large}
  \begin{multicols}{2}
  \begin{flushleft}{\bf Instructor}\end{flushleft}
  \begin{flushright}2021-2022\end{flushright}
  \end{multicols}
  \vspace{-0.17cm}
  \begin{multicols}{2}
    \begin{flushleft}\textit{University of South Carolina}\end{flushleft}
    \begin{flushright}Columbia, SC\end{flushright}
  \end{multicols}
  \end{large}
\vspace{-0.16cm}

\begin{itemize}
\tightlist
\item
  Spring 2024: Introduction to Politics (U)
\item
  Spring 2022: International Relations (U)
\item
  Fall 2021: Comparative Politics (U)
\end{itemize}

\vspace{7pt}
\begin{large}
  {\bf PROFESSIONAL AFFILIATION}
  \vspace{3pt}
  \hrule
  \textit{Graduate Student Membership}
  \end{large}
  \begin{multicols}{2}
    \begin{flushleft}\textit{American Political Science Association}\end{flushleft}
    \begin{flushright}2021-Present\end{flushright}
  \end{multicols}
    \begin{multicols}{2}
    \begin{flushleft}\textit{Midwest Political Science Association}\end{flushleft}
    \begin{flushright}2019-Present\end{flushright}
  \end{multicols}
    \begin{multicols}{2}
    \begin{flushleft}\textit{Southern Political Science Association}\end{flushleft}
    \begin{flushright}2019-Present\end{flushright}
  \end{multicols}
    \begin{multicols}{2}
    \begin{flushleft}\textit{International Studies Association}\end{flushleft}
    \begin{flushright}2021-Present\end{flushright}
  \end{multicols}
    \begin{multicols}{2}
    \begin{flushleft}\textit{Korean Association of Party Studies}\end{flushleft}
    \begin{flushright}2022-Present\end{flushright}
  \end{multicols}

\vspace{7pt}

\begin{large}
  {\bf PROFESSIONAL SERVICE ACTIVITIES}
\end{large}
  \vspace{3pt}
  \hrule
  \begin{multicols}{2}
    \begin{flushleft}International Relations and Comparative Politics Brown Bag\end{flushleft}
    \begin{flushright}2018-Present\end{flushright}
  \end{multicols}
  \begin{multicols}{2}
    \begin{flushleft}\textit{Department of Political Science, UofSC}\end{flushleft}
    \begin{flushright}Columbia, SC\end{flushright}
  \end{multicols}
  \vspace{-0.17cm}

\begin{itemize}
\tightlist
\item
  2018-Present: Presenter and Discussant
\end{itemize}

\begin{multicols}{2}
    \begin{flushleft}The Annual Conference\end{flushleft}
    \begin{flushright}Apr 2022\end{flushright}
  \end{multicols}
  \begin{multicols}{2}
    \begin{flushleft}\textit{Midwest Political Science Association}\end{flushleft}
    \begin{flushright}Chicago, IL\end{flushright}
  \end{multicols}
  \vspace{-0.17cm}

\begin{itemize}
\tightlist
\item
  2022: Chair and Presenter
\end{itemize}

\vspace{7pt}

\begin{large}
  {\bf EXTRA CURRICULUM \& SKILLS}
  \vspace{3pt}
  \end{large}
  \hrule
  \begin{multicols}{2}
    \begin{flushleft}{\bf EITM Summer Institute}\end{flushleft}
    \begin{flushright}June 2021-Jul 2021\end{flushright}
  \end{multicols}
    \begin{multicols}{2}
    \begin{flushleft}{\it University of California, Berkeley}\end{flushleft}
    \begin{flushright}Berkeley, CA\end{flushright}
  \end{multicols}
  \vspace{-0.17cm}

\begin{itemize}
\tightlist
\item
  Causal inference and theoretical models
\item
  Practicum on building theoretical models
\item
  Theory evaluation in experimental, observational, and qualitative
  research
\item
  The role of theory and identification in generalized causal inference
\item
  Theory building and evaluation in comparative politics, international
  relations, political behavior, and political institutions
\end{itemize}

\begin{multicols}{2}
    \begin{flushleft}{\bf ICPSR Summer Program}\end{flushleft}
    \begin{flushright}May 2021\end{flushright}
  \end{multicols}
    \begin{multicols}{2}
    \begin{flushleft}{\it University of Michigan}\end{flushleft}
    \begin{flushright}Ann Arbor, MI\end{flushright}
  \end{multicols}
  \vspace{-0.17cm}

\begin{itemize}
\tightlist
\item
  Network Analysis: Statistical Approach (Short Workshop)
\end{itemize}

\vspace{7pt}

\begin{multicols}{2}
    \begin{flushleft}{\bf ICPSR Summer Program}\end{flushleft}
    \begin{flushright}June 2020-Aug 2020\end{flushright}
  \end{multicols}
    \begin{multicols}{2}
    \begin{flushleft}{\it University of Michigan}\end{flushleft}
    \begin{flushright}Ann Arbor, MI\end{flushright}
  \end{multicols}
  \vspace{-0.17cm}

\begin{itemize}
\item
  First Session: June 22nd-July 17th, 2020

  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \tightlist
  \item
    Bayesian Modeling for the Social Sciences I: Introduction and
    Application
  \item
    Maximum Likelihood Estimation I: Generalized Linear Models
  \item
    Introduction to Python (July 6-17)
  \end{enumerate}
\item
  Second Session: July 20th-August 14th, 2020

  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \tightlist
  \item
    Game Theory
  \item
    Bayesian Modeling for the Social Sciences II: Advanced Topics
  \item
    Causal Inference for the Social Sciences
  \end{enumerate}
\end{itemize}

\vspace{7pt}

\textbf{Computing Skills}: R, STATA, Python, \LaTeX,
\href{https://quarto.org/}{Quarto}, Markdown, Git \&
\href{www.github.com}{Github}

\vspace{7pt}

\textbf{Languages}: Korean (fluent), Japanese (fluent), English (highly
proficient)

\vspace{7pt}
\vspace*{\fill}
\begin{large}
  {\bf REFERENCES}
  \vspace{3pt}
  \end{large}
  \hrule
\begin{tabular}{lr}
% Referee 1
\begin{minipage}[t]{4in}
Prof. Matthew Charles Wilson\\
Political Science\\
University of South Carolina
\Letter\ \href{mailto:WILSO929@mailbox.sc.edu}{WILSO929\textrm{@}mailbox.sc.edu}
\end{minipage}
&
% Referee 2
\begin{minipage}[t]{4in}
Prof. Tobias Heinrich\\
Political Science\\
University of Houston
\Letter\ \href{mailto:theinric@Central.UH.EDU}{theinric\textrm{@}Central.UH.EDU}
\end{minipage}
\\
\\
% Referee 3
\begin{minipage}[t]{4in}
Prof. Howard Liu\\
Political Science\\
University of South Carolina
\Letter\ \href{mailto:HL23@mailbox.sc.edu}{HL23\textrm{@}mailbox.sc.edu}
\end{minipage}
&
% Referee 3
\begin{minipage}[t]{4in}
Prof. Carl Henrik Knutsen\\
Political Science\\
University of Oslo
\Letter\ \href{mailto:c.h.knutsen@stv.uio.no}{c.h.knutsen\textrm{@}stv.uio.no}
\end{minipage}
\end{tabular}

\vspace{5em}

\centering \textit{Last updated: \today}




\end{document}
